Mathematics of Reinforcement Learning with Applications to Quantitative Finance

### 2022-08-22 papers/paper_2-col.tex
update abstract and introduction

%%% Change these to your keywords.  Keywords are automatically printed at the end of the abstract.
%%% This command MUST COME BEFORE the end of the abstract.
%%% If you don't want keywords, leave the argument of \keywords{} empty (or use the abstract* environment)
\keywords{Reinforcement Learning, Artificial Neural Networks}

%% Abstract should be 200 words or less
\begin{abstract}
\noindent Abstract goes here.
\end{abstract}

\section{Introduction}
\noindent The object is to use reinforcement learning to solve the following scenario:
a customer arrives with a number of features, we want to promote the customer
with a proper price, such that he is most likely to purchase our product, and 
we also have the highest profit and a better portfolio. 
\vspace{3mm}\newline We can consider this scenario as markov decision process,
with the current state being the current customer features and current 
portfolio. At each time step, the agent promote a price according to the 
current customer features and the current portfolio, after that the customer 
resopnse to the action. The reward is then given besed on the customer 
response and the portfolio. Then the portfolio updates and a new customer 
arrives.

>>>>

%%% Change these to your keywords.  Keywords are automatically printed at the end of the abstract.
%%% This command MUST COME BEFORE the end of the abstract.
%%% If you don't want keywords, leave the argument of \keywords{} empty (or use the abstract* environment)
\keywords{
    Reinforcement Learning, Artificial Neural Networks, Quantitative Finance
}

%% Abstract should be 200 words or less
\begin{abstract}
\noindent This paper provides a new way of pricing in the car insurance
industry, which is, using reinforcement learning algorithms to train pricing 
agents to promote proper price, such that our customer is most likely to 
purchase our product, and we also get the highest profit and a better 
portfolio. 
We first introduce general reinforcement learning knowledge, including how 
we model the interaction between agent and environment using MDP, and the 
mathematics behind those methods to solve the reinforcement learning problem, 
especially the Actor-Critic algorithm.
Then we start building the environment, and use ANNs as our pricing models, 
and writing algorithms that are specific to our financial problem. 
In the end, we will compare and discuss different algorithms in terms of their
rate of convergence to a stable reward.
\end{abstract}

\section{Introduction}
\noindent Modern way of calculating car insurance premium is by estimating
how much risk the customer poses to the insurance provider, and more risk 
results in higher premium. 
The estimation of the risk for a customer is usually done by comparing various
risk factors with the statistics of the database collected so far. Those 
factors might include customer's age, address, occupation, car's mileage, 
brand and model, and so on. For example, younger drivers pose higher risks 
since they are more likely to have an accident due to the lack of driving 
experience compare to elder drivers.
\vspace{2mm}\newline In this paper, instead of using the above method to 
promote car insurance, we use RL methods to train agents that will interact 
with the market and response with price. More specifically, we consider the 
insurance promoting scenario as markov decision process, with the current 
state being the current customer features and current portfolio. At each time
step, the agent promote a price according to the current customer features and
the current portfolio, after that the customer resopnse to the promotion. The 
reward is then given besed on the customer response and the portfolio. Then 
the portfolio updates and a new customer arrives. This set up will help us to
solve the poblem in the context of reinforcement learning, further details are
discussed in the remaining sections.
